\bf\mftitle

### 2011-02-19 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

@@

TODO obrazok ako Visualizer dedi od VisualizationVieweru a obsahuje Layout.

@@

\begin{itemize}
	\item \code{addGraphMousePlugin()}
	\item \code{removeGraphMousePlugin()}
	\item \code{getGraphMousePlugins()}
	\item \code{setVertexLabelTransformer()}
	\item \code{replaceVertexLabelTransformer()}
	\item \code{setEdgeLabelTransformer()}
	\item \code{replaceEdgeLabelTransformer()}
\end{itemize}

@@

@@

Popis tried pouzitych v inych moduloch, ktore sluzia zaroven ako priklad.

>>>>

TODO UML diagramy su zjednodusene z dovodu prehladnosti

@@

@@

\begin{itemize}
	\item \code{addGraphMousePlugin()}
	\item \code{removeGraphMousePlugin()}
	\item \code{getGraphMousePlugins()}
	\item \code{replaceVertexLabelTransformer()}
	\item \code{replaceEdgeLabelTransformer()}
\end{itemize}

@@

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_basic_full}
\caption{Class diagram for the base classes.} \label{uml_basic_full}
\end{figure}

@@

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_derived_classes}
\caption{Class diagram for the derived classes.} \label{uml_derived_classes}
\end{figure}

This section describes classes derived from the base classes used in \jmodule{Two Step Simplifier} module to display automata. This classes may also serve as examples of extending the base classes.

\subsubsection{StatePickingComponent}
\code{StatePickingComponent} (extensions of \code{abstractComponent}) alongside with \code{StatePickingVisualizer} (extension of \code{PluggableVisualizer}) provides possibility to pick one automaton state in GUI and immediately return to the calling code, which can retrieve the picked state.

\code{StatePickingVisualizer} is trivial extension of \code{PluggableVisualizer}. It has no additional methods. Its constructor has additional two arguments, superinitial and superfinal states as we want to distinguish these states in displayed automaton.\
And upon construction, it just adds \code{VertexPickingGraphMousePlugin} to the plugins of \code{PluggableVisualizer}. Purpose of this plugin is to allow user to pick some state of automaton and then call \code{guiDone()} method on instance of \code{AbstractComponent}. For description of \code{guiDone()} method, see TODO ref.

\code{StatePickingComponent} provides the following additional methods.
\begin{itemize}
	\item \code{getPickedState()} - After displaying the component using \code{drawComponentAndWaitForGUI()} \emph{API} method (see TODO ref), this method retrieves the user picked automaton state.
	\item \code{setLabel()} - Sets text of a component label. The label can be used to communicate some information to user, for example instructions.
\end{itemize}

Source codes of \code{StatePickingComponent} resides in package \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.component}, \code{StatePickingVisualizer} in \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer} and \code{VertexPickingGraphMousePlugin}.

Example of usage follows.
\begin{verbatim}
final Transformer<Step<Regexp<T>>, String> transformer = new Transformer<Step<Regexp<T>>, String>() {

      @Override
      public String transform(final Step<Regexp<T>> step) {
        StringBuilder sb = new StringBuilder();
        sb.append("{");
        sb.append(symbolToString.toString(step.getAcceptSymbol()));
        sb.append("|");
        sb.append(String.valueOf(step.getUseCount()));
        sb.append("}");
        return sb.toString();
      }
    };

    State<Regexp<T>> removeState;
    final StatePickingComponent<Regexp<T>> component = new StatePickingComponent<Regexp<T>>();
    final StatePickingVisualizer<Regexp<T>> visualizer = new StatePickingVisualizer<Regexp<T>>(LayoutHelperFactory.createUserLayout(automaton, transformer), transformer, component, automaton.getSuperInitialState(), automaton.getSuperFinalState());
    component.setVisualizer(visualizer);

    do {
      AutoEditor.drawComponentAndWaitForGUI(component);
      removeState = component.getPickedState();

      if ((removeState.equals(automaton.getSuperFinalState())) || (removeState.equals(automaton.getSuperInitialState()))) {
        component.setLabel("Do not select superInitial and superFinal states.");
        continue;
      }
      LOG.debug("AUTO EDITOR selected: " + removeState.toString());
      return removeState;
    } while (true);
\end{verbatim}
